---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes/media/README-",
  out.width = "100%"
)
```

# readTDMS

<!-- badges: start -->
<!-- badges: end -->

The goal of [readTDMS](https://github.com/abhishekhanchate/readTDMS) is to first of all to read in data stream in an NI TDMS (National Instruments Technical Data Management Streaming) file format and to test the use of R for data processing requirements without making any modifications in the data acquisition procedure. The package provides an intuitive output in the form of a data stream or a time series. It also provides means to perform subsequent analyses such as analysis of the time series data in the time domain, frequency domain, and time-frequency domain along with important metrics and visual plots.

## Installation

[readTDMS](https://github.com/abhishekhanchate/readTDMS) is designed as an R package and we can install it from GitHub via:

``` r
# install.packages("devtools")
devtools::install_github("abhishekhanchate/readTDMS", build_vignettes = TRUE)
```

## Potential Windows Installation Errors

Sometimes, the `install_github` function doesn’t work properly on Windows as it fails to install some of the dependencies. So, you may have to install them manually. Possible dependencies include the following:

```{r, eval=FALSE}
install.packages(c('tdmsreader', 'oce', 'signal', 'ggplot2'))
```

Note that this is only a problem on windows, other platforms should install all dependencies automatically when you use:
\
`devtools::install_github('abhishekhanchate/readTDMS')` 
\
or
\
`library(devtools)`
`install_github('abhishekhanchate/readTDMS')`

## Example

We demonstrate the functionalities of the package [readTDMS](https://github.com/abhishekhanchate/readTDMS) in reading and analyzing data streams coming from a TDMS file. The first step after installing and importing the library is to read a TDMS file from a given repository/directory. (Note: The TDMS_Index file associated with the TDMS file must also be present in the same folder)
\
\
Now, by using the `tdmsread()` function, we can read in the required TDMS file. This function provides us with the extracted data stream in form of the amplitude values of the data as well as the timestamps associated with it. We also get a brief summary of the data stream along with an optional (by default, False) visual into the time domain illustration.

```{r, example, fig.align="center"}
library(readTDMS)
## Basic Example Code
f <- file('./vignettes/data/file.tdms', 'rb')
out <- tdmsread(f, plot = TRUE)
head(out$datastream, n = 15)
head(out$timestamps, n = 15)
out$summ
close(f)
```

For more detailed introduction to the package, please refer [here](https://github.com/abhishekhanchate/readTDMS/blob/master/vignettes/tdms-vignette.pdf) for more details.
\
\
If you encounter any issue with the package, please feel free to file and issue.

## Notes

This package only supports a subset of the TDMS spec and has been tested on single channel 32-bit float data stream. 
\
\
Feedback is welcomed! Please feel free to raise an issue.

## Credit

This package relies on the initial direct reading functionality on the R package, [tdmsreader](https://github.com/msuefishlab/tdmsreader), which in-turn is a port of the Python package, [npTDMS](https://github.com/adamreeve/npTDMS), into R and shares the same LGPL license.
