---
title: "TDMS File Reader and Analyzer"
author: "Abhishek Hanchate"
date: 2021-12-13
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TDMS File Reader and Analyzer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction and Motivation

In this vignette, we go over the readTDMS, an R-based TDMS file format reader and analyzer package which is used for reading a TDMS file and performing subsequent analyses on the extracted data stream. Not a lot of attention or consideration is given to data storage options at forefront of application planning and data storage. Decisions are often made arbitrarily on an as-needed, per-application basis without much thought to reusability, scalability, and recyclability or reproducibility, which leads to tedious and costly software rearchitecture. Given that applications and requirements change over time, even the most popular file storing formats quickly fall short of meeting the demands of engineers and scientists storing time-based measurement data. This is especially common in fields such as smart manufacturing, IoT, and healthcare, wherein large amounts of data is generated without much metadata associated with it. 

## NI TDMS Format

An NI TDMS (National Instruments Technical Data Management Streaming) file format is used for saving well-documented measurement data which is stored in the most efficient, organized, and scalable fashion to disk. Given the fairly complex binary format, these files are often difficult to directly read in R. This package lets us test the use of R for data processing requirements without changing anything with the data acquisition process. Also, having this direct reading process assists in reducing barriers to others trying to use R for such a purpose. The package will have a dependency on [tdmsreader](https://github.com/msuefishlab/tdmsreader) by [msuefishlab](https://github.com/msuefishlab) and contains further analyses and functionalities such as frequency domain visuals as well as time-frequency domain spectral plots. 


```{r setup}
library(readTDMS)
```
